Indicators for Ecosystem Condition in Norway

### 2023-10-04 NDVI_seminat.Rmd
Some erroneos headers

```{r warning=FALSE}
SentinelNDVI.seminat %>%
  filter(year == kartleggingsaar) %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  theme(axis.text.x = element_text(angle = 35, vjust = 1, hjust=1))+
  facet_wrap(~hovedtype)
```

@@

```{r balanced-data-ndvis, warning=FALSE, message=FALSE, fig.cap="NDVI values across a condition gradien, faceted by six semi natural ecosystem types in five regions in Norway. "}
# NDVI across hovedtyper, regions and condition classes (only for NDVI years data matching NiN-mapping years)
SentinelNDVI.seminat %>%
  group_by(id, year) %>%
  filter(year == kartleggingsaar) %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  facet_grid(region ~ hovedtype)
```

@@

# Northern Norway

@@

# Central Norway

```{r central-nvdi-vs-tilstand-ndvis, message=FALSE, warning=FALSE, fig.cap="NDVI agains ecosystm condition for five semi-natural ecosystems in Central Norway."}
SentinelNDVI.seminat.train %>%
  filter(region == "Central Norway") %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  facet_wrap(~hovedtype)
```

@@

# Western Norway

@@

# Eastern Norway

```{r east-nvdi-vs-tilstand-ndvis, message=FALSE, warning=FALSE, fig.cap="NDVI agains ecosystm condition for five semi-natural ecosystems in E-Norway."}
SentinelNDVI.seminat.train %>%
  filter(region == "Eastern Norway") %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  facet_wrap(~hovedtype)
```

@@

# Southern Norway

```{r  south-nvdi-vs-tilstand-ndvis, message=FALSE, warning=FALSE, fig.cap="NDVI agains ecosystm condition for five semi-natural ecosystems in S-Norway."}
SentinelNDVI.seminat.train %>%
  filter(region == "Southern Norway") %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  facet_wrap(~hovedtype)
```

>>>>

```{r ndvi-condition-ndvis, warning=FALSE, fig.cap="NDVI values across semi-natural ecosystem sites in different ecological condition."}
SentinelNDVI.seminat %>%
  filter(year == kartleggingsaar) %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  theme(axis.text.x = element_text(angle = 35, vjust = 1, hjust=1))+
  facet_wrap(~hovedtype)
```

@@

```{r balanced-data-ndvis, warning=FALSE, message=FALSE, fig.cap="NDVI values across a condition gradient, faceted by six semi natural ecosystem types in five regions in Norway. "}
# NDVI across hovedtyper, regions and condition classes (only for NDVI years data matching NiN-mapping years)
SentinelNDVI.seminat %>%
  group_by(id, year) %>%
  filter(year == kartleggingsaar) %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  facet_grid(region ~ hovedtype)
```

@@

**Northern Norway**

@@

**Central Norway**

```{r central-nvdi-vs-tilstand-ndvis, message=FALSE, warning=FALSE, fig.cap="NDVI against ecosystem condition for five semi-natural ecosystems in Central Norway."}
SentinelNDVI.seminat.train %>%
  filter(region == "Central Norway") %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  facet_wrap(~hovedtype)
```

@@

**Western Norway**

@@

**Eastern Norway**

```{r east-nvdi-vs-tilstand-ndvis, message=FALSE, warning=FALSE, fig.cap="NDVI against ecosystem condition for five semi-natural ecosystems in E-Norway."}
SentinelNDVI.seminat.train %>%
  filter(region == "Eastern Norway") %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  facet_wrap(~hovedtype)
```

@@

**Southern Norway**

```{r south-nvdi-vs-tilstand-ndvis, message=FALSE, warning=FALSE, fig.cap="NDVI against ecosystem condition for five semi-natural ecosystems in S-Norway."}
SentinelNDVI.seminat.train %>%
  filter(region == "Southern Norway") %>%
  ggplot(aes(x = tilstand, y = mean)) +
  geom_violin() +
  geom_point(size = 0.7, shape = 16, color = "grey") +
  facet_wrap(~hovedtype)
```
